Risk Perceptions for Wearable Devices

### 2015-01-08 wearables_survey.tex
Small changes to Section 3.2

We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits. We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000. They did this alongside well-establish technologies studied by Fischhoff\etal\cite{Fischhoff}, which we used to calibrate our results. When assessing new technologies, participants generally rated all familiar technologies and those related to wearables as being low-risk. Figure \ref{fig:techplot} depicts participants' median ratings. We found that the calibration technologies were all rated as the most risky. At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.

>>>>

We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits. We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000. To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}. We found that participants generally rated familiar technologies and those related to wearables as being low-risk. Figure~\ref{fig:techplot} depicts participants' median ratings. We found that the calibration technologies were all rated as the most risky. At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
